---
title: "Figure 2C"
output:
  pdf_document: default
  html_document: default
---
Predicting mean growth rate based on predictive model and constructing DFE

Using raw data is more difficult to use for predictive mean growth rate because of missing data point between replicates

Chunk 1: Import packages, data, and set theme.
Chunk 2: Normaliz data using DESeq2 and perform polynomial model fitting.
Chunk 3:

```{r setup, include=FALSE}
#BiocManager::install(organism, character.only = TRUE)

#Library packages
library(tidyverse)
library(DESeq2)
library(patchwork)
library(clusterProfiler)
library(enrichplot)
library("org.Sc.sgd.db", character.only = TRUE)

#Set theme and colors for the entire document
theme_set(theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.text=element_text(size=12),
        axis.title=element_text(size=14), legend.text=element_text(size=12), legend.title=element_text(size=14)))

Clim_col <- "firebrick1"
Nlim_col <- "royalblue2"
Switch_col <- "purple3"
PulseAS_col <- "darkgreen"
PulseGln_col <- "pink"

#Import data
data.directory <- "/Users/farah/Google Drive/Abdul-Rahman et al Barseq/data"
#data.file.name<-paste(data.directory,'/BARseq_Tidy_Clean.txt',sep="")
data.directory <- "/Users/farah/Google Drive File Stream/My Drive/Abdul-Rahman et al Barseq/data"

data.file.name <- paste(data.directory,'/ReplicateFilteredData.txt',sep="")
data <- read.table(file=data.file.name,header=T)

data <- dplyr::select(data, -AdjLibraryCountSums)

data$Data <- "Full"

data_exc <- data %>%
            mutate(YFL021W = ifelse(Condition %in% c("Nlim", "PulseAS", "PulseGln"), 0, YFL021W),
                   YDR277C = ifelse(Condition %in% c("Clim"), 0, YDR277C),
                   YPL056C = ifelse(Condition %in% c("Switch"), 0, YPL056C),
                   YOR091W = ifelse(Condition %in% c("PulseAS"), 0, YOR091W))

data_exc$Data <- "Excluded"

BarSeq1 <- rbind(data, data_exc)
```


```{r}
#Choose conditions
#BarSeq <- data
BarSeqOrd<-BarSeq1[order(BarSeq1$Condition,BarSeq1$TimePoint,
                        BarSeq1$Replicate),]

all_conds <- c("Nlim", "Clim", "Switch","PulseAS","PulseGln")
all_forms <- c("Full", "Excluded")

for (form in all_forms){
  
#  BarSeq<-BarSeqOrd[BarSeq1$Data == form, -dim(BarSeqOrd)[2]]
  
  for (cond in all_conds){
  
  BarSeq<-BarSeqOrd[BarSeqOrd$Data == form, -dim(BarSeqOrd)[2]]
  CD<-BarSeq[BarSeq$Condition == cond, 1:3]
  CD[,"Replicate"]<-as.factor(CD[,"Replicate"])
  CD[,"TimePoint"]<-as.numeric(CD[,"TimePoint"])

  BarSeq[,"Replicate"]<-as.factor(BarSeq[,"Replicate"])
  BarSeq[,"Condition"]<-as.character(BarSeq[,"Condition"])
  BarSeq<-BarSeq[BarSeq$Condition==cond,]
  BarSeq[,"Condition"]<-as.factor(BarSeq[,"Condition"]) #Remove these at the end

  YT<-as.data.frame(BarSeq[BarSeq$Condition==cond,-(1:3)])
  #dim(YT)
  #dim(CD)
  
  Y<-t(YT) #The count matrix is now genotype-by-libraries
  LibSizes<-colSums(Y)
  
#Filter based on counts and library size counts >10, library >1000  
  
  FDR=0.1
  r<-dim(Y)[2]
  SF<-rep(0,r)
  for(i in 1:r){
    J<-which(Y[,i]!=0)
    SF[i]<-exp(mean(log(Y[J,i])))
    }
  sf<-SF/exp(mean(log(SF))) #scale geometric means by the geometric
  
  YnormGM<-Y%*%diag(1/sf)
  
  f<-1/60 #Frequency of the environmental switching
  Sin<-sin(2*pi*f*CD[,"TimePoint"])
  Cos<-cos(2*pi*f*CD[,"TimePoint"])
  CD<-data.frame(CD,Sin,Cos)

  #Identify periodically oscillating genotypes
  ddsPeriodic <- DESeqDataSetFromMatrix(countData = Y,
           colData = CD,
           design = ~ Replicate + TimePoint + Sin + Cos)
  sizeFactors(ddsPeriodic)<-sf #set the sizeFactors to be ours
  ddsPeriodic<-DESeq(ddsPeriodic,fitType='local') #Does the analysis

  ddsAperiodic<-DESeq(ddsPeriodic,test="LRT", reduced=~Replicate+TimePoint)
  resAperiodic<-results(ddsAperiodic)
  sum(resAperiodic$padj<FDR)
#  Jperiodic<- resAperiodic$padj<FDR
  Jperiodic<- which(resAperiodic$padj<FDR)
  
  #Which are not periodic?
  JNotperiodic<- which(resAperiodic$padj>FDR)
  Jna <- length(which(is.na(resAperiodic$padj))) #268, these are samples without enough datapoint to do model fitting
  
  namesPeriodic<-rownames(resAperiodic)[Jperiodic]
  length(namesPeriodic)
  #421

  #Remove genotypes considered periodic and test the rest for cubic behavior
  ddsCubic <- DESeqDataSetFromMatrix(countData = Y[JNotperiodic,], colData = CD,
          design = ~ Replicate+I(TimePoint)+I(TimePoint^2)+I(TimePoint^3))

  sizeFactors(ddsCubic)<-sf #set the sizeFactors to be ours
  ddsCubic<-DESeq(ddsCubic,fitType='local') #Does the analysis
  
  #2.Test for significance of cubic terms by running a reduced model with the cubic term and cubic interactions         removed.

  ddsCubicRed<-DESeq(ddsCubic,test="LRT",fitType='local', reduced=~Replicate+I(TimePoint)+I(TimePoint^2))

  resCubicRed<-results(ddsCubicRed)
  resCubicRed1<-na.omit(resCubicRed)
  sum(resCubicRed1$padj<FDR)
  #[1] 220

  J.cubic<-which(resCubicRed$padj<FDR) #These (indices) have significant cubic terms
  Names.cubic<-rownames(resCubicRed)[J.cubic] #corresponding names

  ddsQuadratic <- DESeqDataSetFromMatrix(countData = Y[JNotperiodic,][-J.cubic,],
                colData = CD,
  design = ~ Replicate+I(TimePoint)+I(TimePoint^2))

  sizeFactors(ddsQuadratic)<-sf #set the sizeFactors to be ours
  ddsQuadratic<-DESeq(ddsQuadratic,fitType='local') #Does the analysis
  
  ddsQuadraticRed<-DESeq(ddsQuadratic,test="LRT", reduced=~Replicate+I(TimePoint))

  resQuadraticRed<-results(ddsQuadraticRed)
  resQuadraticRed1<-na.omit(resQuadraticRed)
  sum(resQuadraticRed1$padj<FDR)
  #[1] 615 the number of genotypes with a significant quadratic term

  J.quadratic<-which(resQuadraticRed$padj<FDR)
  Names.quadratic<-rownames(resQuadraticRed)[J.quadratic]

  J.non.quadratic<-which(!resQuadraticRed$padj<FDR)
  Names.non.quadratic<-rownames(resQuadraticRed)[-J.quadratic]
  length(J.non.quadratic)
  #[1] 2199 Genotypes that are linear, with and without interactions,

  ddsLinear <- DESeqDataSetFromMatrix(countData = 
                Y[JNotperiodic,][-J.cubic,][-J.quadratic,],
                colData = CD,
 design = ~ Replicate+I(TimePoint))

  sizeFactors(ddsLinear)<-sf #set the sizeFactors to be ours
  ddsLinear<-DESeq(ddsLinear,fitType='local') #Does the analysis

  resLinear<-results(ddsLinear,name="I.TimePoint.")
  J.linear<-which(resLinear$padj<FDR)
  Names.linear<-rownames(resLinear)[J.linear] #1267 with timepoint dependence is that true?

  J.non.dependent<-which(!resLinear$padj<FDR)
  Names.non.dependent<-rownames(resLinear)[J.non.dependent] #1096, should be 1313, that is because there are NAs.

#Make normalized abundance df for downstream use 
  ynorm_df <- data.frame(CD[,c(1:3)],t(YnormGM))
  ynorm_df$Data <- form
#  assign(paste(cond, "ynorm", sep = "_"), ynorm_df)
  assign(paste(paste(cond, form, sep = "_"), "ynorm", sep = "_"), ynorm_df)

  
#Make df with behavior type for downstream use
  non.dep_df<-data.frame(Names.non.dependent,"non_significant")
  colnames(non.dep_df)<-c("Strain","Polynomial")

  linear_df<-data.frame(Names.linear,"linear")
  colnames(linear_df)<-c("Strain","Polynomial")

  quadratic_df<-data.frame(Names.quadratic,"quadratic")
  colnames(quadratic_df)<-c("Strain","Polynomial")

  cubic_df<-data.frame(Names.cubic,"cubic")
  colnames(cubic_df)<-c("Strain","Polynomial")

if(length(namesPeriodic) > 0) {          
  periodic_df <- data.frame(namesPeriodic,"periodic")
  colnames(periodic_df) <-c ("Strain","Polynomial")}

  full_model_df1<-rbind(non.dep_df,linear_df)
  full_model_df2<-rbind(full_model_df1,quadratic_df)
  full_model_df<-rbind(full_model_df2,cubic_df)
  if(length(namesPeriodic) > 0) { 
  full_model_df<-rbind(full_model_df,periodic_df)
                                } #total size is 3445 something is missing

  full_model_df$Condition<-cond
  full_model_df$Data <- form
  
#  assign(paste(cond, "full_model", sep = "_"), full_model_df) 
  assign(paste(paste(cond, form, sep = "_"), "full_model", sep = "_"), full_model_df)

    
  model_summary<-full_model_df%>%
    group_by(Polynomial) %>%
      summarise(count=n())
  
  model_summary$Condition<-cond
  
#  assign(paste(cond, "model_summary", sep = "_"),model_summary)  
  assign(paste(paste(cond, form, sep = "_"), "model_summary", sep = "_"), model_summary)

   
#Create coefficients dataframe for downstream use

cols_df <- data.frame(baseMean=NA, log2FoldChange=NA, lfcSE=NA, stat=NA,pvalue=NA,padj=NA)[numeric(0), ]

if(length(namesPeriodic) > 0) {
  periodic_coefs <- data.frame(coef(ddsPeriodic)[namesPeriodic,], resAperiodic[Jperiodic,])
  periodic_coefs$Model<-"Periodic"
  periodic_coefs$Strain<-rownames(periodic_coefs)
  colnames(periodic_coefs)[4] <- "I.TimePoint."} else {
    periodic_coefs <- data.frame(coef(ddsPeriodic)[namesPeriodic,])
    colnames(periodic_coefs)[4] <- "I.TimePoint."
    periodic_coefs <- data.frame(periodic_coefs, cols_df)
  }
  
  cubic_coefs<-data.frame(coef(ddsCubic)[Names.cubic,], resCubicRed[J.cubic,])
  cubic_coefs$Model<-"Cubic"
  cubic_coefs$Strain<-rownames(cubic_coefs)

  quadratic_coefs<-data.frame(coef(ddsQuadratic)[Names.quadratic,], resQuadraticRed[J.quadratic,])
  quadratic_coefs$Model<-"Quadratic"
  quadratic_coefs$Strain<-rownames(quadratic_coefs)

  linear_coefs<-data.frame(coef(ddsLinear)[Names.linear,], resLinear[J.linear,])
  linear_coefs$Model<-"Linear"
  linear_coefs$Strain<-rownames(linear_coefs)

  non_dep_coefs<-data.frame(coef(ddsLinear)[Names.non.dependent,], resLinear[J.non.dependent,])
  non_dep_coefs$Model<-"Non-Significant"
  non_dep_coefs$Strain<-rownames(non_dep_coefs)

  test1<-bind_rows(periodic_coefs,cubic_coefs)
  test2<-bind_rows(test1,quadratic_coefs)
  test3<-bind_rows(test2,linear_coefs)
  full_coefs<-bind_rows(test3,non_dep_coefs) %>%
    replace(is.na(.), 0)
  
  full_coefs$Condition <- cond
  full_coefs$Data <- form

  assign(paste(paste(cond, form, sep = "_"), "coef", sep = "_"), full_coefs)
  }

}
```

Combine dataframes from all conditions
```{r}

full_ynorm_Excluded <- rbind(rbind(rbind(rbind(Nlim_Excluded_ynorm, Switch_Excluded_ynorm), Clim_Excluded_ynorm), PulseAS_Excluded_ynorm), PulseGln_Excluded_ynorm)
full_ynorm_Full <- rbind(rbind(rbind(rbind(Nlim_Full_ynorm, Switch_Full_ynorm), Clim_Full_ynorm), PulseAS_Full_ynorm), PulseGln_Full_ynorm)

full_ynorm <- rbind(full_ynorm_Excluded, full_ynorm_Full)
#full_ynorm <- rbind(rbind(rbind(rbind(Nlim_ynorm, Switch_ynorm), Clim_ynorm), PulseAS_ynorm), PulseGln_ynorm)

full_model_Excluded <- rbind(rbind(rbind(rbind(Nlim_Excluded_full_model, Switch_Excluded_full_model),Clim_Excluded_full_model), PulseAS_Excluded_full_model), PulseGln_Excluded_full_model)
full_model_Full <- rbind(rbind(rbind(rbind(Nlim_Full_full_model, Switch_Full_full_model),Clim_Full_full_model), PulseAS_Full_full_model), PulseGln_Full_full_model)
full_model_conditions <- rbind(full_model_Excluded, full_model_Full)

ggplot(full_model_conditions, aes(x=Condition, fill = Polynomial)) +
  geom_histogram(stat="count") +
  facet_wrap(Data~Polynomial)

full_coefs_Excluded <- rbind(rbind(rbind(rbind(Nlim_Excluded_coef, Switch_Excluded_coef), Clim_Excluded_coef),PulseAS_Excluded_coef), PulseGln_Excluded_coef)
full_coefs_Full <- rbind(rbind(rbind(rbind(Nlim_Full_coef, Switch_Full_coef), Clim_Full_coef),PulseAS_Full_coef), PulseGln_Full_coef)
full_coefs_conditions <- rbind(full_coefs_Excluded, full_coefs_Full)

write_tsv(full_ynorm, paste0(data.directory,"/full_ynorm.txt"))
write_tsv(full_model_conditions, paste0(data.directory,"/full_model_conditions.txt"))
write_tsv(full_coefs_conditions, paste0(data.directory,"/full_coefs_conditions.txt"))

```


Make DF with mean growth rate
```{r cars}
# First and last time points.
t=c(0,240)

# Length of periods
f=1/60

mean_growth_df <- full_coefs_conditions %>%
  mutate(T0_Rep1 = `Intercept`+`I.TimePoint.`*t[1]+`I.TimePoint.2.`*t[1]^2+`I.TimePoint.3.`*t[1]^3+`Sin`*sin(2*pi*f*t[1])+`Cos`*cos(2*pi*f*t[1]),
         T240_Rep1 = `Intercept`+`I.TimePoint.`*t[2]+`I.TimePoint.2.`*t[2]^2+`I.TimePoint.3.`*t[2]^3+`Sin`*sin(2*pi*f*t[2])+`Cos`*cos(2*pi*f*t[2]),
         T0_Rep2 = `Replicate_2_vs_1`+`Intercept`+`I.TimePoint.`*t[1]+`I.TimePoint.2.`*t[1]^2+`I.TimePoint.3.`*t[1]^3+`Sin`*sin(2*pi*f*t[1])+`Cos`*cos(2*pi*f*t[1]),
         T240_Rep2 = `Replicate_2_vs_1`+`Intercept`+`I.TimePoint.`*t[2]+`I.TimePoint.2.`*t[2]^2+`I.TimePoint.3.`*t[2]^3+`Sin`*sin(2*pi*f*t[2])+`Cos`*cos(2*pi*f*t[2]),
         T0_Rep3 = `Replicate_3_vs_1`+`Intercept`+`I.TimePoint.`*t[1]+`I.TimePoint.2.`*t[1]^2+`I.TimePoint.3.`*t[1]^3+`Sin`*sin(2*pi*f*t[1])+`Cos`*cos(2*pi*f*t[1]),
         T240_Rep3 = `Replicate_3_vs_1`+`Intercept`+`I.TimePoint.`*t[2]+`I.TimePoint.2.`*t[2]^2+`I.TimePoint.3.`*t[2]^3+`Sin`*sin(2*pi*f*t[2])+`Cos`*cos(2*pi*f*t[2]),
         T0_mean = rowMeans(cbind(T0_Rep1, T0_Rep2, T0_Rep3), na.rm = TRUE),
         T240_mean = rowMeans(cbind(T240_Rep1, T240_Rep2, T240_Rep3), na.rm = TRUE)) %>%
          mutate(MeanGrowthRate=(T240_mean-T0_mean)/240)

#For geomtric mean growth rate:
#From Figure3.Rmd
#geometric mean function

#gm_mean = function(x, na.rm=TRUE){
#  exp(sum(log(x[x > 0]), na.rm=na.rm) / 240) #I divided by 240 instead of length(x) because that is the number of hours
#}

#gm_test <- full_ynorm_gathered %>%
#  group_by(Condition, Replicate, Strain) %>%
#    mutate(GeoMeanGrowth = gm_mean(Ynorm),
#           ArithmeticMeanGrowth = mean(Ynorm)) %>%
#      dplyr::select(-TimePoint, -Ynorm) %>%
#        distinct() %>%
#          group_by(Condition, Strain) %>%
#            mutate(MeanGeoMeanGrowth = mean(GeoMeanGrowth),
#                   MeanArithmeticMeanGrowth = mean(ArithmeticMeanGrowth)) %>%
#                     dplyr::select(-Replicate, -GeoMeanGrowth, -ArithmeticMeanGrowth) %>%
#                       distinct()

#gm_test2 <- mean_growth_df %>%
#  dplyr::select(Strain, Condition, MeanGrowthRate) %>%
#    left_join(., gm_test, by = c("Strain", "Condition"))

#ggplot(gm_test2, aes(x = MeanArithmeticMeanGrowth, y = MeanGrowthRate)) +
#  geom_point() +
#  scale_x_log10() +
#  scale_y_log10()

```

Test piecewise growth and different intervals for growth rate measurements
```{r}
#Should this be deleted?
test <- full_ynorm %>%
  gather(Strain, y_norm, -TimePoint, -Condition, -Replicate, -Data) %>%
    group_by(Condition, Replicate, Strain, Data) %>%
      mutate(PW_GR = (y_norm - lag(y_norm))/(TimePoint - lag(TimePoint))) %>%
        dplyr::select(-y_norm) %>%
          group_by(Condition, TimePoint, Data) %>%
            mutate(Mean_RelativeFitness = mean(PW_GR)) %>%
             ungroup() %>%
              complete(TimePoint, Condition, Replicate, Data, fill = list(0))

#ggplot(filter(test, Replicate == 1, Condition %in% c("Clim","Nlim","Switch")), aes(x = Condition, y = PW_GR, group = Condition, fill = factor(stat(quantile)))) +
#  stat_density_ridges(
#    geom = "density_ridges_gradient",
#    calc_ecdf = TRUE,
#    quantiles = c(0.025, 0.975))
#  geom_histogram(bins = 40, color = "black",aes(y=count_frequency)) +
#  geom_density_ridges(aes(fill = Condition))
```


```{r pressure, echo=FALSE}
#Plot the DFEs for 
#ggplot(mean_growth_df, aes(x=MeanGrowthRate)) +
#  geom_histogram() +
#  facet_wrap(~Condition)

#Make binned table and plot the binned DFE
bin_limits <- seq(0, 0.054, by= 0.002)
hist_breaks <- c(-rev(bin_limits[-1]), bin_limits)

mode <- function(x) {
     ux <- unique(x)
     ux[which.max(tabulate(match(x, ux)))]
 }
#Table_MG_Summary <- Table_MG %>%
#  group_by(Condition, bins) %>%
#    dplyr::summarise(sum_freq = sum(count_frequency),
#                   n=n(),
#                   sum_mean_freq = sum(mean_strain_freq))

#Get stats for mean growth rate
Stat_table_MG <- mean_growth_df %>%
    group_by(Condition, Data) %>%
     summarise(Mode = mode(MeanGrowthRate), Median = median(MeanGrowthRate), Mean = mean(MeanGrowthRate), Max = max(MeanGrowthRate), Min = min(MeanGrowthRate), Variance = var(MeanGrowthRate)) %>%
       mutate(Range = Max - Min)

#Trying to get the proportions, check where NAs are coming from
#adjTest <- data %>%
#  select(-DOWN, -UP, -Tag_Ratio) %>%
#   spread(Replicate, as.numeric(Sum_Tag)) %>%
#     mutate(across(c(`1`, `2`, `3`), na_if, 0))
#    replace(is.na(.), 0) %>%
#       mutate(adjSumTag = `1`+`2`+`3`) %>%
        #replace(is.na(.), 0) %>% 
#         group_by(Condition, TimePoint) %>%  
#          mutate(adjLibSize = sum(adjSumTag, na.rm=T),
#                  adjCountProp = adjSumTag/adjLibSize) %>%
#             ungroup() %>%
#               select(TimePoint, Condition, Strain, adjCountProp) %>%
#                 spread(TimePoint, adjCountProp) %>%
#                    inner_join(mean_growth_df, by = c("Condition", "Strain")) %>%
#                      group_by(Condition) %>%
#                        arrange(MeanGrowthRate) %>%
#                          mutate(bins = cut(MeanGrowthRate, breaks=hist_breaks)) %>%
#                            group_by(Condition, bins) %>%
#                              mutate(Prop_t0 = sum(`0`, na.rm=T),
#                                     Prop_t240 = sum(`240`, na.rm=T),
#                                     Delta_Prop_Pct = (Prop_t240 - Prop_t0)*100,
#                                     n=n())


# Make table with proportions and mean growth rates
adjTest <- BarSeq1 %>%
  filter(Data == "Full") %>%
  dplyr::select(-Data) %>%
  gather(key = Strain, value = Sum_Tag, -TimePoint, -Condition, -Replicate) %>%
    group_by(TimePoint, Condition, Replicate) %>%
      mutate(LibrarySize = sum(Sum_Tag, na.rm=T),
             Proportion = Sum_Tag/LibrarySize) %>%
        dplyr::select(-Sum_Tag, -LibrarySize) %>%
          mutate(Proportion = as.numeric(na_if(Proportion, 0))) %>%
            spread(Replicate, Proportion) %>%
              rowwise() %>%
                mutate(MeanProportion = (mean(c(`1`, `2`, `3`), na.rm=T))) %>%
                 dplyr::select(-`1`, -`2`, -`3`) %>%
                   spread(TimePoint, MeanProportion) %>%#fine
                    inner_join(mean_growth_df, by = c("Condition", "Strain")) %>%
                      group_by(Condition) %>%
                        arrange(MeanGrowthRate) %>%
                          mutate(bins = cut(MeanGrowthRate, breaks=hist_breaks)) %>%
                            group_by(Condition, bins) %>%
                              mutate(Prop_t0 = sum(`0`, na.rm=T),
                                     Prop_t240 = sum(`240`, na.rm=T),
                                     Delta_Prop_Pct = (Prop_t240 - Prop_t0)*100,
                                     n=n())


#Make x-axis labels for bar plot
hist_breaks_labels <- hist_breaks
hist_breaks_labels[c(2:4, 6:9, 11:14, 16:19, 21:24, 26:29, 31:34, 36:39, 41:44, 46:49, 51:54)] <- ''
#hist_breaks_labels[seq(2, length(hist_breaks_labels), by = 2)] <- ''


#Plot DFE across three condition
p1 <- ggplot(filter(adjTest, Condition %in% c("Nlim","Clim","Switch"), Data == "Full")) +
  geom_bar(stat = "identity", position = position_dodge(), aes(x = bins, y = n, fill = Condition), color = "black") +
  facet_wrap(~Condition) +
  scale_x_discrete(labels = c(0.05, 0.03), breaks = c(0.05,0.03), drop=FALSE) +
  scale_fill_manual(values=c(Clim_col, Nlim_col, Switch_col)) +
  xlab("Growth Rate (hr-1)") +
  ylab("Genotype Frequency") +
  theme(axis.text=element_text(size=12),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        axis.title=element_text(size=14),
        legend.text=element_text(size=12),
        legend.title=element_text(size=14),
        panel.background = element_rect(fill = "white",
                                        colour = "black",
                                        size = 0.75, linetype = "solid"),
        panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        strip.text.x = element_blank())

p2  <- ggplot(filter(adjTest, Condition %in% c("Nlim","Clim","Switch"), Data == "Full")) +
  geom_bar(stat = "identity", position = position_dodge(), aes(x = bins, y = Delta_Prop_Pct, fill = Condition), color = "black") +
  facet_wrap(~Condition) +
  scale_x_discrete(labels = hist_breaks_labels, drop=FALSE) +
  scale_fill_manual(values=c(Clim_col, Nlim_col, Switch_col)) +
  xlab("Growth Rate (hr-1)") +
  ylab("Percent Change in Population Proportion") +
  theme(axis.text=element_text(size=12),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        axis.title=element_text(size=14),
        legend.title=element_text(size=14),
        panel.background = element_rect(fill = "white",
                                        colour = "black",
                                        size = 0.75, linetype = "solid"),
        panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        panel.grid.major.x = element_line(size = 0.25, colour = "white"),
        panel.grid.major.y = element_line(size = 0.25, colour = "gray"),
        strip.text.x = element_blank())


#pdf("/Users/farah/Google Drive/Abdul-Rahman et al Barseq/figures/Figure2/Figure2C", width=12, height=6)

p <- p1 + p2 + plot_layout(ncol=1,heights=c(2,2))

ggsave(plot = p, height=9, width=12, dpi=200, filename="/Users/farah/Google Drive/Abdul-Rahman et al Barseq/figures/Figure2/Figure2C.pdf", useDingbats=FALSE)

####Supplementary including pulse
p3 <- ggplot(filter(adjTest, Condition %in% c("Nlim","Clim", "PulseAS", "PulseGln", "Switch"), Data == "Full")) +
  geom_bar(stat = "identity", position = position_dodge(), aes(x = bins, y = n, fill = Condition), color = "black") +
  facet_wrap(~Condition, ncol=5) +
  scale_x_discrete(labels = hist_breaks_labels, drop=FALSE) +
  scale_fill_manual(values=c(Clim_col, Nlim_col, PulseAS_col, PulseGln_col, Switch_col)) +
  xlab("Growth Rate (hr-1)") +
  ylab("Genotype Frequency") +
  theme(axis.text=element_text(size=12),
        panel.grid.major.x = element_line(size = 0.25, colour = "white"),
        panel.grid.major.y = element_line(size = 0.25, colour = "gray"),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        axis.title=element_text(size=14),
        legend.text=element_text(size=12),
        legend.title=element_text(size=14),
        panel.background = element_rect(fill = "white",
                                        colour = "black",
                                        size = 0.75, linetype = "solid"),
        panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        strip.text.x = element_blank())

p4  <- ggplot(filter(adjTest, Condition %in% c("Nlim","Clim", "PulseAS", "PulseGln", "Switch"), Data == "Full")) +
  geom_bar(stat = "identity", position = position_dodge(), aes(x = bins, y = Delta_Prop_Pct, fill = Condition), color = "black") +
  facet_wrap(~Condition, ncol=5) +
  scale_x_discrete(labels = hist_breaks_labels, drop=FALSE) +
  scale_fill_manual(values=c(Clim_col, Nlim_col, PulseAS_col, PulseGln_col, Switch_col)) +
  xlab("Growth Rate (hr-1)") +
  ylab("Percent Change in Population Proportion") +
  theme(axis.text=element_text(size=12),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        axis.title=element_text(size=14),
        legend.text=element_text(size=12),
        legend.title=element_text(size=14),
#        panel.background = element_rect(fill = "white",
#                                        colour = "black",
#                                        size = 0.75, linetype = "solid"),
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_line(size = 0.25, colour = "white"),
        panel.grid.major.y = element_line(size = 0.25, colour = "gray"),
        strip.background = element_blank(),
        strip.text.x = element_blank())

p <- p3 + p4 + plot_layout(ncol=1,heights=c(2,2))

ggsave(plot = p, height=9, width=15, dpi=200, filename="/Users/farah/Google Drive/Abdul-Rahman et al Barseq/supplement/figures/Figure2C-1.pdf", useDingbats=FALSE)
 
```


Testing the effect of strain number over time
```{r}
#Looking at the change in strains represented over time
#adjTest_gathered <- adjTest %>%
#  gather(TimePoint, Proportion, `0`, `24`, `48`, `72`, `96`, `120`, `144`, `168`, `192`, `240`)

#TotalStrain_df <- adjTest_gathered %>%
#  group_by(TimePoint, Condition, Data) %>%
#    filter(!is.na(Proportion)) %>%
#      filter(Data == "Full") %>%
#       mutate(TotalStrainNumber = n())

#p5 <- ggplot(TotalStrain_df, aes(x = as.numeric(TimePoint), y = TotalStrainNumber, color = Condition)) +
#  geom_line() +
#  geom_point() +
#  scale_color_manual(values=c(Clim_col, Nlim_col, PulseAS_col, PulseGln_col, Switch_col)) +
#  ylim(0, 4000) +
#  ylab("Total Strain Number") +
#  xlab("Time (hrs)") 
#  facet_wrap(~Condition)

#ggsave(plot = p5, height=3, width=4, dpi=200, filename="/Users/farah/Google Drive/Abdul-Rahman et al Barseq/supplement/figures/Figure2C-2.pdf", useDingbats=FALSE)

#dev.off()  
#Testing a different df for strain number with all three replicates

Strain_Number <- BarSeqOrd %>%
  gather(Strain, Norm_Count, -TimePoint, -Replicate, -Condition, -Data) %>%
    dplyr::filter(Norm_Count > 0, Data == "Full") %>%
      group_by(TimePoint, Condition, Replicate) %>%
          summarise(TotalStrainNumber = n())
          
p5 <- ggplot(Strain_Number, aes(x = as.numeric(TimePoint), y = TotalStrainNumber, color = Condition, shape = as.character(Replicate))) +
  geom_smooth(method = "lm", aes(group=Condition)) +
  geom_point() +
  scale_color_manual(values=c(Clim_col, Nlim_col, PulseAS_col, PulseGln_col, Switch_col)) +
  ylim(0, 4000) +
  ylab("Total Strain Number") +
  xlab("Time (hrs)") +
  facet_wrap(~Condition, ncol = 5) +
  theme(strip.background = element_blank())

ggsave(plot = p5, height=3, width=15, dpi=200, filename="/Users/farah/Google Drive/Abdul-Rahman et al Barseq/supplement/figures/suppfig5.pdf", useDingbats=FALSE)


```

Make dataframe of extinct genotypes for each condition
```{r}
BiocManager::install("upSetR", character.only = TRUE)
BiocManager::install("ComplexHeatmap", character.only = TRUE)
#library(VennDiagram)
library("upSetR")
library("ComplexHeatmap")

#data starts with 3906 total strains
#test <-data %>%      
#        filter(TimePoint == 240) %>%

test <- TotalStrain_df %>%
            ungroup() %>%
              filter(TimePoint == 240) %>%
                dplyr::select(Condition, Strain, TotalStrainNumber, T240_mean) %>%
                  tidyr::spread(Strain, T240_mean) %>%
                    gather(Strain, T240_mean_ynorm, -Condition, -TotalStrainNumber)

test1 <- test %>%
  group_by(Condition) %>%
    filter(is.na(T240_mean_ynorm)) %>%
      dplyr::select(-T240_mean_ynorm, -TotalStrainNumber) %>%
        mutate(count = 1) %>%
          spread(Condition, count) %>%
            as.data.frame() %>%
              replace(is.na(.), 0)
  
rownames(test1) <- test1$Strain
test1 <- test1[, -1]

col_list<-as.list(c("darkgoldenrod4", "goldenrod3", "lightgoldenrod2", "black"))
m = make_comb_mat(test1)
UpSet(m, top_annotation = HeatmapAnnotation(
	degree = as.character(comb_degree(m)),
	col = list(degree = c("1" = "darkgoldenrod4", "2" = "goldenrod3", "3" = "lightgoldenrod2", "4" = "black")),
	"Intersection\nsize" = anno_barplot(comb_size(m), 
		border = FALSE, 
		gp = gpar(fill = "black"), 
		height = unit(2, "cm")
	), 
	annotation_name_side = "left", 
	annotation_name_rot = 0),
	comb_col = c("darkgoldenrod4", "goldenrod3", "lightgoldenrod2", "black")[comb_degree(m)], left_annotation = rowAnnotation(
	"Set size" = anno_barplot(set_size(m), 
		border = FALSE,
		gp = gpar(fill = c(Clim_col, Nlim_col, PulseAS_col,PulseGln_col, Switch_col), col = FALSE), 
		width = unit(2, "cm")
	)), right_annotation = NULL)

#test making matrix where columns are conditions, and rows are strains and presence or absence is 0 and 1

#Downstream overrepresentation analysis

```

#Violin plots that show the change in genotype fitness
#Decide whether this should be included in the paper or not
```{r}
library(ggrepel)

violin_GR <- mean_growth_df %>%
  filter(Data == "Full") %>%
  dplyr::select(Condition, Strain, MeanGrowthRate) %>%
  mutate(Condition = fct_relevel(Condition, c("Nlim", "Switch", "Clim")))

top_clim_performers <- violin_GR %>%
  filter(Condition %in% c("Clim", "Switch")) %>%
  filter(Strain %in% c("YDR277C", "YLR006C", "YLR113W")) %>%
  mutate(Condition = fct_relevel(Condition, c("Switch", "Clim")))

top_nlim_performers <- violin_GR %>%
  filter(Condition %in% c("Nlim", "Switch")) %>%
  filter(Strain %in% c("YFL021W", "YCR095C", "YLR386W")) %>%
  mutate(Condition = fct_relevel(Condition, c("Nlim", "Switch")))

low_clim_performers <- violin_GR %>%
  filter(Condition %in% c("Clim", "Switch")) %>%
  filter(Strain %in% c("YGR193C", "YKL168C", "YAL049C", "YDR048C", "YMR111C")) %>%
  mutate(Condition = fct_relevel(Condition, c("Switch", "Clim")))

low_nlim_performers <- violin_GR %>%
  filter(Condition %in% c("Nlim", "Switch")) %>%
  filter(Strain %in% c("YOL004W", "YEL061C", "YGR092W", "YEL033W", "YDR225W")) %>%
  mutate(Condition = fct_relevel(Condition, c("Nlim", "Switch")))


ggplot(filter(violin_GR, Condition %in% c("Clim", "Switch", "Nlim")), aes(x = Condition, y = MeanGrowthRate, color = Condition, fill = Condition)) +
  geom_violin(trim = F, alpha = 0.3) +
  geom_boxplot(width=0.07, fill="white", outlier.size = 0, alpha = 0.7) +
  geom_text_repel(data=top_clim_performers, aes(label=Strain), col = "black", size=3) +
  geom_line(data=top_clim_performers, aes(group = Strain, color = Condition), alpha = 0.5) +
  geom_text_repel(data=top_nlim_performers, aes(label=Strain), col = "black", size=3) +
  geom_line(data=top_nlim_performers, aes(group = Strain, color = Condition)) +
  geom_line(data=low_nlim_performers, aes(group = Strain, color = Condition)) +
  geom_line(data=low_clim_performers, aes(group = Strain, color = Condition))
  
  
  
```


Perform gene-set-enrichment
```{r}
organism <- "org.Sc.sgd.db"

GOterm_baseList <- data %>%
   dplyr::select(-TimePoint, -Condition, -Replicate) %>%
      colnames()

#geneList <- as.character(GOterm_baseList[-3907,])

annotations_orgDb <- AnnotationDbi::select(org.Sc.sgd.db, # database
                                     keys = (GOterm_baseList),
                                     columns = c("ENSEMBL", "GENENAME"), #information to retreive for given data
                                     keytype = "ENSEMBL") # type of data given in 'keys' argument

GO_df <- adjTest %>%
              ungroup() %>%
                dplyr::select(Condition, Strain, MeanGrowthRate) %>%
                  distinct()

Switch_gene_list <- GO_df %>%
                      filter(Condition == "Switch") %>%
                        dplyr::select(MeanGrowthRate) %>%
                          unlist()
                          
        
names(Switch_gene_list) <- GO_df %>%
                      filter(Condition == "Switch") %>%
                        dplyr::select(Strain) %>%
                          unlist()
  
# omit any NA values 
#Switch_gene_list<-na.omit(Switch_gene_list)
# sort the list in decreasing order (required for clusterProfiler)
Switch_gene_list = sort(Switch_gene_list, decreasing = TRUE)

gse_Switch <- gseGO(geneList = Switch_gene_list, 
             ont ="ALL", 
             keyType = "ENSEMBL", 
             nPerm = 10000, 
             minGSSize = 3, 
             maxGSSize = 800, 
             pvalueCutoff = 0.05, 
             verbose = TRUE, 
             OrgDb = organism, 
             pAdjustMethod = "none")

g1 <- enrichplot::dotplot(gse_Switch, showCategory=10, split=".sign") + facet_grid(.~.sign)

Clim_gene_list <- GO_df %>%
                      filter(Condition == "Clim") %>%
                        dplyr::select(MeanGrowthRate) %>%
                          unlist()
                          
        
names(Clim_gene_list) <- GO_df %>%
                      filter(Condition == "Clim") %>%
                        dplyr::select(Strain) %>%
                          unlist()
  
# omit any NA values 
#Switch_gene_list<-na.omit(Switch_gene_list)
# sort the list in decreasing order (required for clusterProfiler)
Clim_gene_list = sort(Clim_gene_list, decreasing = TRUE)

gse_Clim <- gseGO(geneList = Clim_gene_list, 
             ont ="ALL", 
             keyType = "ENSEMBL", 
             nPerm = 10000, 
             minGSSize = 3, 
             maxGSSize = 800, 
             pvalueCutoff = 0.05, 
             verbose = TRUE, 
             OrgDb = organism, 
             pAdjustMethod = "none")

g2 <- enrichplot::dotplot(gse_Clim, showCategory=10, split=".sign") + facet_grid(.~.sign)

Nlim_gene_list <- GO_df %>%
                      filter(Condition == "Nlim") %>%
                        dplyr::select(MeanGrowthRate) %>%
                          unlist()
                          
        
names(Nlim_gene_list) <- GO_df %>%
                      filter(Condition == "Nlim") %>%
                        dplyr::select(Strain) %>%
                          unlist()
  
# omit any NA values 
#Switch_gene_list<-na.omit(Switch_gene_list)
# sort the list in decreasing order (required for clusterProfiler)
Nlim_gene_list = sort(Nlim_gene_list, decreasing = TRUE)

gse_Nlim <- gseGO(geneList = Nlim_gene_list, 
             ont ="ALL", 
             keyType = "ENSEMBL", 
             nPerm = 10000, 
             minGSSize = 3, 
             maxGSSize = 800, 
             pvalueCutoff = 0.05, 
             verbose = TRUE, 
             OrgDb = organism, 
             pAdjustMethod = "none")

g3 <- enrichplot::dotplot(gse_Nlim, showCategory=10, split=".sign") + facet_grid(.~.sign)

PulseAS_gene_list <- GO_df %>%
                      filter(Condition == "PulseAS") %>%
                        dplyr::select(MeanGrowthRate) %>%
                          unlist()
                          
        
names(PulseAS_gene_list) <- GO_df %>%
                      filter(Condition == "PulseAS") %>%
                        dplyr::select(Strain) %>%
                          unlist()
  
# sort the list in decreasing order (required for clusterProfiler)
PulseAS_gene_list = sort(PulseAS_gene_list, decreasing = TRUE)

gse_PulseAS <- gseGO(geneList = PulseAS_gene_list, 
             ont ="ALL", 
             keyType = "ENSEMBL", 
             nPerm = 10000, 
             minGSSize = 3, 
             maxGSSize = 800, 
             pvalueCutoff = 0.05, 
             verbose = TRUE, 
             OrgDb = organism, 
             pAdjustMethod = "none")

g4 <- enrichplot::dotplot(gse_PulseAS, showCategory=10, split=".sign") + facet_grid(.~.sign)

PulseGln_gene_list <- GO_df %>%
                      filter(Condition == "PulseGln") %>%
                        dplyr::select(MeanGrowthRate) %>%
                          unlist()
                          
        
names(PulseGln_gene_list) <- GO_df %>%
                      filter(Condition == "PulseGln") %>%
                        dplyr::select(Strain) %>%
                          unlist()
  
# sort the list in decreasing order (required for clusterProfiler)
PulseGln_gene_list = sort(PulseGln_gene_list, decreasing = TRUE)

gse_PulseGln <- gseGO(geneList = PulseGln_gene_list, 
             ont ="ALL", 
             keyType = "ENSEMBL", 
             nPerm = 10000, 
             minGSSize = 3, 
             maxGSSize = 800, 
             pvalueCutoff = 0.05, 
             verbose = TRUE, 
             OrgDb = organism, 
             pAdjustMethod = "none")

g5 <- enrichplot::dotplot(gse_PulseGln, showCategory=10, split=".sign") + facet_grid(.~.sign)


#Merge data sets
num <- 8 #Number of selected GO term

gse_Nlim_df1 <- arrange(gse_Nlim[,], desc(NES))
gse_Nlim_df <- rbind(head(gse_Nlim_df1, n = num), tail(gse_Nlim_df1, n = num))

gse_Clim_df1 <- arrange(gse_Clim[,], desc(NES))
gse_Clim_df <- rbind(head(gse_Clim_df1, n = num), tail(gse_Clim_df1, n = num))

gse_Switch_df1 <- arrange(gse_Switch[,], desc(NES))
gse_Switch_df <- rbind(head(gse_Switch_df1, n = num), tail(gse_Switch_df1, n = num))

gse_PulseAS_df1 <- arrange(gse_PulseAS[,], desc(NES))
gse_PulseAS_df <- rbind(head(gse_PulseAS_df1, n = num), tail(gse_PulseAS_df1, n = num))

gse_PulseGln_df1 <- arrange(gse_PulseGln[,], desc(NES))
gse_PulseGln_df <- rbind(head(gse_PulseGln_df1, n = num), tail(gse_PulseGln_df1, n = num))

gse_Nlim_df$Condition = "Nlim"
gse_Clim_df$Condition = "Clim"
gse_Switch_df$Condition = "Switch"
gse_PulseAS_df$Condition = "PulseAS"
gse_PulseGln_df$Condition = "PulseGln"

full_GO <- rbind(rbind(rbind(rbind(gse_Nlim_df, gse_Clim_df), gse_Switch_df), gse_PulseAS_df), gse_PulseGln_df)

full_GO$type = "increased fitness"
full_GO$type[full_GO$NES < 0] = "decreased fitness" 

full_GO <- full_GO %>% 
  mutate(Condition = fct_relevel(Condition, c("Nlim", "Switch", "Clim", "PulseAS", "PulseGln"))) %>%
    mutate(core_enrichment = fct_relevel(core_enrichment, sort)) #sort is supposed to relvel the description, needs a better way to group categories based on slim categories, but for now it's okay.


#Test
#dot_df = gse_PulseGln[,] ## small dataset
#dot_df$type = "upregulated"
#dot_df$type[dot_df$NES < 0] = "downregulated"

g <- ggplot(full_GO, aes(x = Condition, y = Description)) + 
               geom_point(aes(size = setSize, color = type)) +
               theme_bw(base_size = 14) +
#        scale_colour_gradient(limits=c(-3, 3), low="red") +
        ylab(NULL) +
        ggtitle("GO pathway enrichment")

#p + facet_grid(.~type)

ggsave(plot = g, height=10, width=14, dpi=200, filename="/Users/farah/Google Drive/Abdul-Rahman et al Barseq/supplement/figures/Figure2C-3.pdf", useDingbats=FALSE)

#end of suppl figure for GO terms


Nlim_gene_list <- GO_df %>%
                      filter(Condition == "Nlim") %>%
                        dplyr::select(MeanGrowthRate) %>%
                          unlist()

Nlim_gene_list = sort(Nlim_gene_list, decreasing = TRUE)

gse_Nlim <- gseGO(geneList =Nlim_gene_list, 
             ont ="ALL", 
             keyType = "ENSEMBL", 
             nPerm = 10000, 
             minGSSize = 3, 
             maxGSSize = 800, 
             pvalueCutoff = 0.05, 
             verbose = TRUE, 
             OrgDb = organism, 
             pAdjustMethod = "none")

p <- p1 + p2 + plot_layout(ncol=1,heights=c(2,2))

ggsave(plot = p, height=6, width=8, dpi=200, filename="/Users/farah/Google Drive/Abdul-Rahman et al Barseq/figures/Figure2/Figure2C.pdf", useDingbats=FALSE)
                          
        
names(Nlim_gene_list) <- GO_df %>%
                      filter(Condition == "Nlim") %>%
                        dplyr::select(Strain) %>%
                          unlist() %>%
                            clusterProfiler::bitr(., fromType="ENSEMBL", toType="ENTREZID", OrgDb = "org.Sc.sgd.db") %>%
  dplyr::select(ENTREZID)

# omit any NA values 
#Switch_gene_list<-na.omit(Switch_gene_list)
# sort the list in decreasing order (required for clusterProfiler)
Nlim_gene_list = sort(Nlim_gene_list, decreasing = TRUE)

gse_Nlim <- gseGO(geneList = Nlim_gene_list, 
             ont ="ALL", 
             keyType = "ENSEMBL", 
             nPerm = 10000, 
             minGSSize = 3, 
             maxGSSize = 800, 
             pvalueCutoff = 0.05, 
             verbose = TRUE, 
             OrgDb = organism, 
             pAdjustMethod = "none")

p <- p1 + p2 + plot_layout(ncol=1,heights=c(2,2))

ggsave(plot = p, height=6, width=8, dpi=200, filename="/Users/farah/Google Drive/Abdul-Rahman et al Barseq/figures/Figure2/Figure2C.pdf", useDingbats=FALSE)
```

