---
title: "Figure1"
output:
  pdf_document: default
  html_document: default
---

---
title: "Figure_1"
author: "Farah"
start date: "6/4/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---
The goal of this document is to generate 'Figure 1' of the BARseq paper. This figure defines the environment in switching conditions based on both modelling approaches and empirical data.

Chunk 1: Import packages and files, set theme
Chunk 2: Analyze empirical data
Chunk 3: generates Switch conditions from AS-lim to Glu-lim

Each of these chunks will display 4 panels 1) AS levels, 2) Glu levels, 3) Cell Density, 4) Growth rate.

```{r}
#Load packages
library(deSolve)
library(tidyverse)

#Set theme and colors for the entire document
theme_set(theme_bw()+theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()))
Clim_col <- "firebrick1"
Nlim_col <- "royalblue2"
Switch_col <- "purple3"
PulseAS_col <- "darkgreen"
PulseGln_col <- "pink"

#Cell density data
Cell_density_data <- read_tsv("/Users/farah/Google Drive/Abdul-Rahman et al Barseq/data/Cell_Counts_Switch1.tsv")

Cell_data <- Cell_density_data[,1:13] %>%
  gather(Sample, Cell_Density, -TimePoint, -Date, -Hour,-Time) %>%
   separate(Sample,into=c("Condition", "Replicate")) %>%
     filter(Cell_Density != "NA")

#Carbon data
Carbon_data <- read_csv("/Users/farah/Google Drive/Abdul-Rahman et al Barseq/data/Glucose_Assay_Full_20190905.csv")

#Nitrogen data
Nitrogen_data <- read_csv("/Users/farah/Google Drive/Abdul-Rahman et al Barseq/data/Nitrogen_Assay_FA_20190616.csv")

```


```{r}
#Nitrogen analysis
#Standard Values
Nitrogen_Std <- c(1, 0.5, 0.25, 0)

#Standard Slope and intercept
Slope <- summary(lm(Nitrogen_data$Fluorescence[1:4] ~ Nitrogen_Std))$coefficients[[2]]
Intercept <- summary(lm(Nitrogen_data$Fluorescence[1:4] ~ Nitrogen_Std))$coefficients[[1]]

#plot(Nitrogen_Std, Nitrogen_data$Fluorescence[1:4])
#abline(b = Slope, a = Intercept)

Nitrogen_data <- Nitrogen_data[c(5:49),] %>%
  separate(Condition, into = c("TimePoint", "Media", "Replicate", "Dilution"), sep = "_")

Time_Hours <- c(rep(c(-2.5, 17, 35, 44, 59.5, 75.5),3), rep(c(0,15,45,75),6))

Blank <- Nitrogen_data$Fluorescence[4]
Time_Post <- c(rep(5,10), rep(15, 6), rep(30, 6))

Nitrogen_Concentration <- Nitrogen_data %>%
  mutate(Norm_Fluo_mM = ( Fluorescence - Blank ) / Slope) %>%
    mutate(Times_Diln = (Norm_Fluo_mM * as.numeric(Dilution))) %>%
      mutate(Norm_Fluo_Diln_uM = Times_Diln*500) %>%
        filter(TimePoint != "T9")

ggplot(Nitrogen_Concentration, aes(y = Times_Diln, x = Time_Hours, color = Media)) +
  geom_rect(aes(xmin = 0, xmax = 30, ymin = -Inf, ymax = Inf), fill = "pink", alpha = 0.01,linetype=0) +
  geom_rect(aes(xmin = 60, xmax = 75, ymin = -Inf, ymax = Inf), fill = "pink", alpha = 0.01,linetype=0) +
  geom_rect(aes(xmin = -2, xmax = 0, ymin = -Inf, ymax = Inf), fill = "steelblue1", alpha = 0.01,linetype=0) +
  geom_rect(aes(xmin = 30, xmax = 60, ymin = -Inf, ymax = Inf), fill = "steelblue1", alpha = 0.01,linetype=0) +
  #scale_color_manual(values = c("lightcoral", "slateblue2", "darkorchid4")) +
  scale_color_manual(values = c(Clim_col, Nlim_col, Switch_col)) +
  geom_point(aes(shape = Replicate)) +
  geom_smooth() +
  xlim(-2.5, 75) +
  ylab("Ammonium Concentration (mM)") +
  xlab("Time (Hours)") +
#  geom_line(lwd = 1.5) +
#  geom_vline(xintercept=c(30,60), lty = 4) +
  scale_x_continuous(breaks=c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65, 70, 75)) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))

#Carbon analysis
Carbon_data <- Carbon_data %>% 
  mutate(Blanked = Step2 - Step1) %>%
   mutate(Normalized = Blanked * 0.8636)

#Check that blank is 0.5 g/L and if not obtain normalization factor to multiply samples and standards by it
Carbon_Std <- Carbon_data %>%
  filter(Sample == "KitControl")

Cntrl_Factor <- as.matrix(0.5/Carbon_Std[1,7])

Carbon_data <- Carbon_data %>%
  mutate(ControlNorm = as.vector(Normalized) * as.vector(Cntrl_Factor))

Standards <- Carbon_data %>%
  filter(grepl("Standard", Sample))

#Visualize standards. Standard curves are proportional with the exception of 2 samples which will be excluded from the analysis. Since the values for these two samples are negative, they don't even appear on the graph below where the limits are starting at 0.
ggplot(Standards, aes(x = Expected, y = ControlNorm, color = as.character(Replicate))) +
  geom_point() +
  geom_smooth(method = "lm") +
  ylim(-1,1) +
  xlim(0,1) +
  ylab("Observed Carbon Concentration (g/L)") +
  xlab("Expected Carbon Concentration (g/L)")

#Obtain slope from standards
Slope <- coef(lm(ControlNorm ~ Expected, data = Standards))[2]

#Process samples
Carbon_concentration <- Carbon_data %>%
  mutate(Std_Norm = ControlNorm * Slope) %>%
    mutate(Final_Concentration = Std_Norm * DilnFactor) %>%
      filter(!grepl("Standard|Blank|Control|EMPTY",Sample)) %>%
        mutate(Molarity = (Final_Concentration/180.16)*1000000) #uM

#ggplot(Carbon_concentration, aes(x = TimePoint, y = Std_Norm, color = Sample)) +
#  geom_point() +
  #geom_smooth(method = "lm") +
  #ylim(0,1) +
  #xlim(0,1) +
  #ylab("Observed Carbon Concentration (g/L)") +
  #xlab("TimePoint")

ggplot(Carbon_concentration, aes(x = TimeHrs, y = Final_Concentration, color = Sample)) +
  geom_point() +
  #geom_smooth(method = "lm") +
  #ylim(0,1) +
  #xlim(0,1) +
  ylab("Observed Carbon Concentration (g/L)") +
  xlab("Time (Hrs)") +
  geom_rect(aes(xmin = 0, xmax = 30, ymin = -Inf, ymax = Inf), fill = "pink", alpha = 0.01,linetype=0) +
  geom_rect(aes(xmin = 60, xmax = 90, ymin = -Inf, ymax = Inf), fill = "pink", alpha = 0.01,linetype=0) +
  geom_rect(aes(xmin = -2, xmax = 0, ymin = -Inf, ymax = Inf), fill = "steelblue1", alpha = 0.01,linetype=0) +
  geom_rect(aes(xmin = 30, xmax = 60, ymin = -Inf, ymax = Inf), fill = "steelblue1", alpha = 0.01,linetype=0) +
  #scale_color_manual(values = c("lightcoral", "slateblue2", "darkorchid4")) +
  scale_color_manual(values = c(Clim_col, Nlim_col, Switch_col)) +
  geom_point(aes(shape = as.character(Replicate))) +
  geom_smooth()


```


Model with no cellular consumption
```{r fig1, fig.height = 15, fig.width = 15}
#Set parameters
parms <- c(
  t <- seq(from = 0, to = 271, by = 1), #hrs
  Ks_AS <- 51.5, #51.5 uM, saturation constant, substrate concentration at which u = 1/2 u_max,
  Ks_G <- 500.5, # uM, saturation constant, substrate concentration at which u = 1/2 u_max,
  Y_AS <- 42500, # cells/mL/uM, 37500 yield constant. The culture yield per mole of the limiting nutrient  
  Y_G <- 13511.6876, # cells/mL/uM, *13511.6876 I'm gonna play with this number and say 6E7cells/mL/4440.6uM Molarity of glucose not carbon
  ss_lag <- -30, # hrs, This is the time the culture was grown in steady state before starting the flucs
  u_max <- 0.35 , # growth/hour, 0.35,  0.005833333 growth/min
  D <- 0.12, # hr-1, At 0.12hr-1 would be 24 mL/hour
  R_s <- 800, # uM, AS concentration in carboy of AS-limiting media
  R_g <- 111014.9, # uM, glucose concentration in carboy of AS-limiting media 
  static_xini <- c(s_AS = R_s, s_G = R_g, X = 0, Growth_Rate = 0) #Initial values AS, glucose concentrations in carboys, and cell density.
)

#Create the function with the system of equations
Sys_func <- function(times, Total, parms) {
  with(as.list(Total, parms), {
  
    #This is the system of equations used to model AS, glucose, and cell density. A modified form of the Michaelis-Mentin equation is used here, to take into consideration two nutrients instead of just one.
      deriv_S <- -s_AS*D + R_s*D - (X/Y_AS) * u_max * 1/(1+(Ks_AS/s_AS)+(Ks_G/s_G))
      
      deriv_G <- -s_G*D + R_g*D - (X/Y_G) * u_max * 1/(1+(Ks_AS/s_AS)+(Ks_G/s_G))
      
      Growth_Rate <- u_max *  1/(1+(Ks_AS/s_AS) + (Ks_G/s_G))
      
      deriv_X   <-  Growth_Rate * X - D * X 
    
    return(list(c(deriv_S, deriv_G, deriv_X, Growth_Rate)))
  
  })
}

#Solving the system of equations.
out_stat_nlim <- ode(y = static_xini, times = t, func = Sys_func, parms=parms)
colnames(out_stat_nlim)<-c("Time (hrs)","Ammonium-Sulfate Concentration (uM)","Glucose Concentration (uM)","Cell Density (cells/mL)","Growth Rate (hr-1)")

#Make change in growth rate function
hist <- function(history_out) {
  history <- list(1:dim(history_out)[1])
  
for (i in 1:271) {
  diff <-history_out[c(i+1),5] - history_out[c(i),5]
  history[i] <- diff #Growth rate hr-1
}
  return(history)  
}

#Calculate change in growth rate
history_stat_nlim <- hist(out_stat_nlim)

out_stat_nlim <- as.data.frame(cbind(out_stat_nlim[1:271,c(1:4)],unlist(history_stat_nlim)))
out_stat_nlim$Condition <- "Nlim"
colnames(out_stat_nlim)[5] <- "Growth Rate (hr-1)" 

#Plotting results
Tidy_Stat_Nlim <- gather(as.data.frame(out_stat_nlim), key = Variable, value = Value, -`Time (hrs)`, -Condition)

#Here, I have tried logging the data but the nummbers were very unintuitive and the trend looked almost exactly the same, so it did not seem useful to do this.
#ggplot(Tidy_Stat_Nlim, aes(x= ss_lag + `Time (hrs)`, y=Value, color=Variable)) + 
#  scale_color_manual(values=c("darkblue", "black","darkred","orange")) +
#  xlab("Time (hours)") +
#  scale_x_continuous(labels = ss_lag + seq(0, 270, 30), breaks = ss_lag + seq(0, 270, 30), expand = c(0, 0)) +
#  facet_wrap(~Variable, ncol=1, scales="free") +
#  geom_vline(xintercept=(c(30,60,90,120,150,180,210,240)), linetype='dashed') +
#  geom_line(size=1.5) +
#  theme(axis.text=element_text(size=16),
#        axis.title.y=element_blank(),
#        axis.title.x=element_text(size=20,face="bold"),
#        legend.text=element_text(size=16),
#        legend.title=element_text(size=20,face="bold"),
#        panel.grid = element_blank(),
#        panel.border = element_blank(),
#        panel.background = element_rect(fill = "white",
#                                        colour = "black",
#                                        size = 0.75, linetype = "solid"),
#        panel.grid.major = element_line(size = 0.25, linetype = 'blank',
#                                        colour = "gray"), 
#        panel.grid.minor = element_line(size = 0.25, linetype = 'blank',
#                                        colour = "gray"),
#        strip.text = element_text(size = 20))

#Static modelling for static Clim
#Set parameters
parms <- c(
  t <- seq(from = 0, to = 271, by = 1), #hrs
  Ks_AS <- 51.5, #51.5 uM, saturation constant, substrate concentration at which u = 1/2 u_max,
  Ks_G <- 500.5, # uM, saturation constant, substrate concentration at which u = 1/2 u_max,
  Y_AS <- 42500, # cells/mL/uM, 37500 yield constant. The culture yield per mole of the limiting nutrient  
  Y_G <- 13511.6876, # cells/mL/uM, *13511.6876 I'm gonna play with this number and say 6E7cells/mL/4440.6uM Molarity of glucose not carbon
  ss_lag <- -30, # hrs, This is the time the culture was grown in steady state before starting the flucs
  u_max <- 0.35 , # growth/hour, 0.35,  0.005833333 growth/min
  D <- 0.12, # hr-1, At 0.12hr-1 would be 24 mL/hour
  R_s <- 37838.7, # uM, AS concentration in carboy of glu-limiting media
  R_g <- 4440.6, # uM, glucose concentration in carboy of glu-limiting media 
  static_xini <- c(s_AS = R_s, s_G = R_g, X = 0, Growth_Rate = 0) #Initial values AS, glucose concentrations in carboys, and cell density.
)

#Create the function with the system of equations
Sys_func <- function(times, Total, parms) {
  with(as.list(Total, parms), {
  
    #This is the system of equations used to model AS, glucose, and cell density. A modified form of the Michaelis-Mentin equation is used here, to take into consideration two nutrients instead of just one.
      deriv_S <- -s_AS*D + R_s*D - (X/Y_AS) * u_max * 1/(1+(Ks_AS/s_AS)+(Ks_G/s_G))
      
      deriv_G <- -s_G*D + R_g*D - (X/Y_G) * u_max * 1/(1+(Ks_AS/s_AS)+(Ks_G/s_G))
      
      Growth_Rate <- u_max *  1/(1+(Ks_AS/s_AS) + (Ks_G/s_G))
      
      deriv_X   <-  Growth_Rate * X - D * X 
    
    return(list(c(deriv_S, deriv_G, deriv_X, Growth_Rate)))
  
  })
}

#Solving the system of equations.
out_stat_clim <- ode(y = static_xini, times = t, func = Sys_func, parms=parms)
colnames(out_stat_clim)<-c("Time (hrs)","Ammonium-Sulfate Concentration (uM)","Glucose Concentration (uM)","Cell Density (cells/mL)","Growth Rate (hr-1)")

#Calculate change in growth rate
history_stat_clim <- hist(out_stat_clim)

out_stat_new_clim <-as.data.frame(cbind(out_stat_clim[1:271,c(1:4)],unlist(history_stat_clim)))
out_stat_new_clim$Condition <- "Clim"
colnames(out_stat_new_clim)[5] <- "Growth Rate (hr-1)" 

#Plotting results
Tidy_Stat_Clim <- gather(as.data.frame(out_stat_new_clim), key = Variable, value = Value, -`Time (hrs)`, -Condition)

#ggplot(Tidy_Stat_Clim, aes(x= ss_lag + `Time (hrs)`, y=Value, color=Variable)) +  #Here, I have tried logging the data but the nummbers were very unintuitive and the trend looked almost exactly the same, so it did not seem useful to do this.
#  scale_color_manual(values=c("darkblue", "black","darkred","orange")) +
#  xlab("Time (hours)") +
#  scale_x_continuous(labels = ss_lag + seq(0, 270, 30), breaks = ss_lag + seq(0, 270, 30), expand = c(0, 0)) +
#  facet_wrap(~Variable, ncol=1, scales="free") +
#  geom_vline(xintercept=(c(30,60,90,120,150,180,210,240)), linetype='dashed') +
#  geom_line(size=1.5) +
#  theme(axis.text=element_text(size=16),
#        axis.title.y=element_blank(),
#        axis.title.x=element_text(size=20,face="bold"),
#        legend.text=element_text(size=16),
#        legend.title=element_text(size=20,face="bold"),
#        panel.grid = element_blank(),
#        panel.border = element_blank(),
#        panel.background = element_rect(fill = "white",
#                                        colour = "black",
#                                        size = 0.75, linetype = "solid"),
#        panel.grid.major = element_line(size = 0.25, linetype = 'blank',
#                                        colour = "gray"), 
#        panel.grid.minor = element_line(size = 0.25, linetype = 'blank',
#                                        colour = "gray"),
#        strip.text = element_text(size = 20))

#Switch conditions

parms <- c(
  t <- seq(from = 0, to = 271, by = 1), #hrs
  Ks_AS <- 51.5, #51.5 uM, saturation constant, substrate concentration at which u = 1/2 u_max,
  Ks_G <- 51.5, # uM, saturation constant, substrate concentration at which u = 1/2 u_max,
  Y_AS <- 42500, # cells/mL/uM, 37500 yield constant. The culture yield per mole of the limiting nutrient  
  #Y_AS <- 13511.6876,
  Y_G <- 13511.6876, # cells/mL/uM, *13511.6876 I'm gonna play with this number and say 6E7cells/mL/4440.6uM Molarity of glucose not carbon
  ss_lag <- -30, # hrs, This is the time the culture was grown in steady state before starting the flucs
  u_max <- 0.35 , # growth/hour, 0.35,  0.005833333 growth/min
  D <- 0.12, # hr-1, At 0.12hr-1 would be 24 mL/hour
  R_ASL_AS <- 800, # uM, AS concentration in carboy of AS-limiting media
  R_GL_AS <- 37838.7, # uM, AS concentration in carboy of glucose-limiting media
  R_ASL_G <- 111014.9, # uM, glucose concentration in carboy of AS-limiting media 
  R_GL_G <- 4440.6, # uM, glucose concentration in carboy of glucose-limiting media
  AS_GL_xini <- c(s_AS = R_GL_AS, s_G = R_GL_G, X = 0, Growth_Rate = 0) #Initial values AS, glucose concentrations in carboys, and cell density.
)

#Create the function with the system of equations
Sys_func <- function(times, Total, parms) {
  with(as.list(Total, parms), {
    
    #The modulus form was used to enable periodic oscillations between glucose-limiting and AS-limiting media every 30 hours.
        if (times > 30 & times %% 60 <= 30)
      { 
      R_s = R_GL_AS
      R_g = R_GL_G
    }else{
      R_s = R_ASL_AS
      R_g = R_ASL_G
      
      
    }

    #This is the system of equations used to model AS, glucose, and cell density. A modified form of the Michaelis-Mentin equation is used here, to take into consideration two nutrients instead of just one.
      deriv_S <- -s_AS*D + R_s*D - (X/Y_AS) * u_max * 1/(1+(Ks_AS/s_AS)+(Ks_G/s_G))
      
      deriv_G <- -s_G*D + R_g*D - (X/Y_G) * u_max * 1/(1+(Ks_AS/s_AS)+(Ks_G/s_G))
      
      Growth_Rate <- u_max *  1/(1+(Ks_AS/s_AS) + (Ks_G/s_G))
      
      deriv_X   <-  Growth_Rate * X - D * X 
    
    return(list(c(deriv_S, deriv_G, deriv_X, Growth_Rate)))
  
  })
}

#Solving the system of equations.
out_switch <- ode(y = AS_GL_xini, times = t, func = Sys_func, parms=parms)
colnames(out_switch)<-c("Time (hrs)","Ammonium-Sulfate Concentration (uM)","Glucose Concentration (uM)","Cell Density (cells/mL)","Growth Rate (hr-1)")

#Make change in growth rate function
hist <- function(history_out) {
  history <- list(1:dim(history_out)[1])
  
for (i in 1:270) {
  diff <-history_out[c(i+1),5] - history_out[c(i),5]
  history[i] <- diff #Growth rate hr-1
}
  return(history)  
}

#Get growth rate...
history_switch <- hist(out_switch)
history <- list(1:dim(out_switch)[1])

#doubling_history <- log(2)/unlist(history)

out_switch_new <- as.data.frame(cbind(out_switch[1:271,c(1:4)],c(0,unlist(history_switch))))
out_switch_new$Condition <- "Switch"
colnames(out_switch_new)[5] <- "Growth Rate (hr-1)"

#Plotting results
Tidy_Switch <- gather(as.data.frame(out_switch_new), key = Variable, value = Value, -`Time (hrs)`, -Condition)

#ggplot(Tidy_Switch, aes(x= ss_lag + `Time (hrs)`, y=Value, color=Variable)) +  #Here, I have tried logging the data but the nummbers were very unintuitive and the trend looked almost exactly the same, so it did not seem useful to do this.
#  scale_color_manual(values=c("darkblue", "black","darkred","orange")) +
#  xlab("Time (hours)") +
#  scale_x_continuous(labels = ss_lag + seq(0, 270, 30), breaks = ss_lag + seq(0, 270, 30), expand = c(0, 0)) +
#  facet_wrap(~Variable, ncol=1, scales="free") +
#  geom_vline(xintercept=(c(30,60,90,120,150,180,210,240)), linetype='dashed') +
#  geom_line(size=1.5) +
#  theme(axis.text=element_text(size=16),
#        axis.title.y=element_blank(),
#        axis.title.x=element_text(size=20,face="bold"),
#        legend.text=element_text(size=16),
#        legend.title=element_text(size=20,face="bold"),
#        panel.grid = element_blank(),
#        panel.border = element_blank(),
#        panel.background = element_rect(fill = "white",
#                                        colour = "black",
#                                        size = 0.75, linetype = "solid"),
#        panel.grid.major = element_line(size = 0.25, linetype = 'blank',
#                                        colour = "gray"), 
#        panel.grid.minor = element_line(size = 0.25, linetype = 'blank',
#                                        colour = "gray"),
#        strip.text = element_text(size = 20))

#Combine this data and add a "No Consumption" tag

#NoConsumption <- rbind(Tidy_Switch, Tidy_Stat_Nlim, Tidy_Stat_glu)
#NoConsumption$CellConsumption <- "No Consumption"
#NoConsumption$Replicate <- "NA"
#This is currently from a different script to combine empirical data with the model

#Combined_Metabolites <- gather(Combined_Metabolites, Variable, Value, -Condition, -Replicate, -`Time (hrs)`)
#Combined_Metabolites$CellConsumption <- "Empirical"
#Combined_Metabolites <- Combined_Metabolites[,c(3,1,4,5,6,2)]

# NoConsumption_SpecialTime <- NoConsumption %>%
#  mutate(`Time (hrs)` = `Time (hrs)` - 60)
 

#Empirical_NoCons <- rbind(NoConsumption_SpecialTime,Combined_Metabolites)

#Empirical_NoCons_Spread <- spread(Empirical_NoCons, Variable,  Value)

#Plot both empirical and model data.
```

#This chunk is for importing and analyzing the glucose and nitrogen empirical data
```{r}
#Cell denisty data
ggplot(Cell_data, aes(x = Hour, y = Cell_Density, color = Condition)) +
  geom_rect(aes(xmin = 0, xmax = 30, ymin = -Inf, ymax = Inf), fill = "pink", alpha = 0.01,linetype=0) +
  geom_rect(aes(xmin = 60, xmax = 90, ymin = -Inf, ymax = Inf), fill = "pink", alpha = 0.01,linetype=0) +
  geom_rect(aes(xmin = -2, xmax = 0, ymin = -Inf, ymax = Inf), fill = "steelblue1", alpha = 0.01,linetype=0) +
  geom_rect(aes(xmin = 30, xmax = 60, ymin = -Inf, ymax = Inf), fill = "steelblue1", alpha = 0.01,linetype=0) +
  scale_color_manual(values = c("black", "darkgray", "white")) +
  geom_point(aes(shape = Replicate)) +
#  geom_line() +
#  stat_smooth(method = "mean") +
  stat_summary(aes(y = Cell_Density, group = Condition), fun.y=mean, geom = "line") +
  geom_vline(xintercept=c(30,60,90), lty = 4) +
  scale_x_continuous(breaks=c(0, 5, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65, 70, 75, 80, 85, 90)) +
 theme_bw()

#Combine empirical and model data

# Make a dataframe of both carbon and nitrogen concentrations + metadata.
#Nitrogen_Combine <- Nitrogen_Concentration[,c(2,3,8)]
Nitrogen_Time <- c(rep(Carbon_concentration$TimeHrs[1:6],3),rep(Carbon_concentration$TimeHrs[c(1,2,4,6)],6))
Nitrogen_df <- cbind(Nitrogen_Concentration[,c(2,3,8)],Nitrogen_Time,rep("Ammonium-Sulfate Concentration (uM)",42))

colnames(Nitrogen_df)[c(1,3,4,5)] <- c("Condition","Concentration","Time (hrs)","Variable")

#Carbon_Combine <- Carbon_concentration[,c(2,3,15,5)]
Carbon_df <- cbind(Carbon_concentration[,c(2,3,15,5)], rep("Glucose Concentration (uM)",63))
colnames(Carbon_df)[c(1,3,4,5)] <- c("Condition","Concentration","Time (hrs)","Variable")

NC_df <- rbind(Nitrogen_df, Carbon_df) %>%
           spread(Variable, Concentration) %>%
             gather(Variable, Value, -Condition, -Replicate, -`Time (hrs)`)

NC_df$CellConsumption <- "Empirical"
NC_df <- NC_df[,c(3,1,4,5,6,2)]
#NC_df$Condition <- sub("Carbon", "Static Glucose", NC_df$Condition)
#NC_df$Condition <- sub("Nitrogen", "Static Nlim", NC_df$Condition)

##### Making full dataframe of empirical and modelled observations
NoConsumption_Model <- rbind(Tidy_Switch, Tidy_Stat_Nlim, Tidy_Stat_Clim)  %>%
                         mutate(`Time (hrs)` = `Time (hrs)` - 60)
NoConsumption_Model$CellConsumption <- "No Consumption"
NoConsumption_Model$Replicate <- "NA"

#NC_df <- gather(NC_df, Variable, Value, -Condition, -Replicate, -`Time (hrs)`)
#NC_df <- NC_df[,c(2,6,3,4,5,1)]

#NoConsumption_SpecialTime <- NoConsumption %>%
#  mutate(`Time (hrs)` = `Time (hrs)` - 60)
 
Emp_Mod_df <- rbind(NoConsumption_Model, NC_df) %>%
                spread(Variable, Value)
  
Emp_Mod_df$Condition <- sub("Carbon", "Clim", Emp_Mod_df$Condition)
Emp_Mod_df$Condition <- sub("Nitrogen", "Nlim", Emp_Mod_df$Condition)

#Empirical_NoCons_Spread <- spread(Empirical_NoCons, Variable, Value)

```

Modelling no consumption plot
```{r}

p1 <- ggplot(Emp_Mod_df, aes(x=`Time (hrs)`, y=`Ammonium-Sulfate Concentration (uM)`, lty= CellConsumption)) +

    geom_rect(data = filter(Emp_Mod_df, Condition == "Clim"), aes(xmin = -5, xmax = 80, ymin = -Inf, ymax = Inf), fill = Clim_col, alpha = 0.01,linetype=0) +  
  
    geom_rect(data = filter(Emp_Mod_df, Condition == "Nlim"), aes(xmin = -5, xmax = 80, ymin = -Inf, ymax = Inf), fill = Nlim_col, alpha = 0.01,linetype=0) + 
   
    geom_rect(data = filter(Emp_Mod_df, Condition == "Switch"), aes(xmin = 0, xmax = 30, ymin = -Inf, ymax = Inf), fill = Clim_col, alpha = 0.01,linetype=0) +
  
    geom_rect(data = filter(Emp_Mod_df, Condition == "Switch"),aes(xmin = 30, xmax = 60, ymin = -Inf, ymax = Inf), fill = Nlim_col ,linetype=0) +
  
    geom_rect(data = filter(Emp_Mod_df, Condition == "Switch"),aes(xmin = 60, xmax = 80, ymin = -Inf, ymax = Inf), fill = Clim_col, alpha = 0.01,linetype=0) +
  
  geom_rect(data = filter(Emp_Mod_df, Condition == "Switch"),aes(xmin = -5, xmax = 0, ymin = -Inf, ymax = Inf), fill = Nlim_col, linetype=0) +
  
  xlab("Time (hours)") +
  
#  geom_line(data = filter(Emp_Mod_df, CellConsumption == "No Consumption"), aes( y = `Ammonium-Sulfate Concentration (uM)`, color = "Nitrogen Concentration"), lwd = 1, color = "blue", lty = "dashed") +
 
  geom_line(data = filter(Emp_Mod_df, CellConsumption == "No Consumption"),aes(`Time (hrs)`,`Ammonium-Sulfate Concentration (uM)`), color = "black", fill = "black", lty = "dashed", lwd = 1) +

  geom_line(data = filter(Emp_Mod_df, CellConsumption == "No Consumption"), aes(`Time (hrs)`,`Glucose Concentration (uM)`/2.95), color = "white",  fill = "white", lty = "dashed", lwd = 1) +
 
#  geom_line(data = filter(Emp_Mod_df, CellConsumption == "No Consumption"), aes(`Time (hrs)`,`Glucose Concentration (uM)`/3), color = "red", lwd = 1, lty = "dashed") +

#  scale_x_continuous(labels = seq(0, 270, 30), breaks = seq(0, 270, 30), expand = c(0, 0)) +
  
  scale_y_continuous(sec.axis = sec_axis(~.*2.95, name = "Glucose Concentration (uM)")) +
  
  scale_color_manual(values=c("white", "black")) +
  
  ylab("Ammonium-Sulfate Concentration (uM)") +
  
  xlab("Time (Hrs)") +
  
  facet_wrap(~Condition, ncol = 3) +
  
  scale_x_continuous(limits = c(-5, 80), expand = c(0, 0)) +
#  ylim(-1000,40000) +  
  
  theme_classic()

pdf("/Users/farah/Google Drive/Abdul-Rahman et al Barseq/figures/Figure1/Figure1B", width=14, height=4)

p1

dev.off()  


```


Empirical data with cellular consumption plot
```{r}

p2 <- ggplot(Emp_Mod_df, aes(x=`Time (hrs)`, y=`Ammonium-Sulfate Concentration (uM)`, lty= CellConsumption)) +

    geom_rect(data = filter(Emp_Mod_df, Condition == "Clim"), aes(xmin = -5, xmax = 80, ymin = -Inf, ymax = Inf), fill = Clim_col, alpha = 0.01,linetype=0) +  
  
    geom_rect(data = filter(Emp_Mod_df, Condition == "Nlim"), aes(xmin = -5, xmax = 80, ymin = -Inf, ymax = Inf), fill = Nlim_col, alpha = 0.01,linetype=0) + 
   
    geom_rect(data = filter(Emp_Mod_df, Condition == "Switch"), aes(xmin = 0, xmax = 30, ymin = -Inf, ymax = Inf), fill = Clim_col, alpha = 0.01,linetype=0) +
  
    geom_rect(data = filter(Emp_Mod_df, Condition == "Switch"),aes(xmin = 30, xmax = 60, ymin = -Inf, ymax = Inf), fill = Nlim_col ,linetype=0) +
  
    geom_rect(data = filter(Emp_Mod_df, Condition == "Switch"),aes(xmin = 60, xmax = 80, ymin = -Inf, ymax = Inf), fill = Clim_col, alpha = 0.01,linetype=0) +
  
  geom_rect(data = filter(Emp_Mod_df, Condition == "Switch"),aes(xmin = -5, xmax = 0, ymin = -Inf, ymax = Inf), fill = Nlim_col, linetype=0) +
  
  xlab("Time (hours)") +
  
#  geom_line(data = filter(Emp_Mod_df, CellConsumption == "No Consumption"), aes( y = `Ammonium-Sulfate Concentration (uM)`, color = "Nitrogen Concentration"), lwd = 1, color = "blue", lty = "dashed") +
 
  geom_smooth(data = filter(Emp_Mod_df, CellConsumption == "Empirical"),aes(`Time (hrs)`,`Ammonium-Sulfate Concentration (uM)`), color = "black", method = "loess", fill = "black") +
  
  geom_point(data = filter(Emp_Mod_df, CellConsumption == "Empirical"), aes( y = `Ammonium-Sulfate Concentration (uM)`, color = "Nitrogen Concentration")) +  
   
  geom_smooth(data = filter(Emp_Mod_df, CellConsumption == "Empirical"), aes(`Time (hrs)`,`Glucose Concentration (uM)`/2.3), color = "white", method="loess", fill = "white") +
 
  geom_point(data = filter(Emp_Mod_df, CellConsumption == "Empirical"), aes(y =`Glucose Concentration (uM)`/2.3, color = "Glucose Concentration"),size=1) +
   
#  geom_line(data = filter(Emp_Mod_df, CellConsumption == "No Consumption"), aes(`Time (hrs)`,`Glucose Concentration (uM)`/3), color = "red", lwd = 1, lty = "dashed") +

#  scale_x_continuous(labels = seq(0, 270, 30), breaks = seq(0, 270, 30), expand = c(0, 0)) +
  
  scale_y_continuous(sec.axis = sec_axis(~.*2.3, name = "Glucose Concentration (uM)")) +
  
  scale_color_manual(values=c("white", "black")) +
  
  ylab("Ammonium-Sulfate Concentration (uM)") +
  
  xlab("Time (Hrs)") +
  
  facet_wrap(~Condition, ncol=3) +
  
#  geom_vline(xintercept=(c(30,60)), linetype='dashed') +
  scale_x_continuous(limits = c(-5, 80), expand = c(0, 0)) +
#  ylim(-1000,40000) +  
  theme_classic()

pdf("/Users/farah/Google Drive/Abdul-Rahman et al Barseq/figures/Figure1/Figure1C", width=14, height=4)

p2

dev.off()  

```


