---
title: "Figure5"
output: html_document
---

#Make violin plot with a subgroup of functions
```{r setup, include=FALSE}
#From Figure 2C

#Library packages
library(ggrepel)

#Set theme and colors for the entire document
theme_set(theme_bw() + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.text=element_text(size=12), axis.title=element_text(size=14), legend.text=element_text(size=12), legend.title=element_text(size=14)))

#Read in data
PW_GR.sim.model <- read_tsv("/Users/farah/Google Drive/Abdul-Rahman et al Barseq in fluctuating environments/scripts/PW_GR.sim.txt")

violin_PW_GR <- PW_GR.sim.model %>%
  dplyr::select( Strain, Model, Time.Sim, Clim, Nlim, Switch, Avg_CN) %>%
    gather(Condition, GR, -Strain, -Model, -Time.Sim) %>%
      group_by(Time.Sim, Condition) %>%
        mutate(Variance = var(GR, na.rm = TRUE))

violin_PW_GR_var <- violin_PW_GR %>%
  group_by(Time.Sim, Condition) %>%
    mutate(Variance = var(GR, na.rm = TRUE))

j1 <- ggplot(filter(violin_PW_GR, Condition %in% c("Clim", "Nlim", "Switch")), aes(x = as.factor(Time.Sim), y = GR, color = Condition, fill = Condition)) +
  geom_violin(trim = F, alpha = 0.3) +
  facet_wrap(~Condition) +
  ylab("Piecewise fitness") +
  xlab("Time (hrs)") +
  scale_color_manual(values = c(Clim_col, Nlim_col, Switch_col)) +
  scale_fill_manual(values = c(Clim_col, Nlim_col, Switch_col)) +
  theme(strip.background = element_blank(), strip.text.y = element_blank())


#  geom_text_repel(data=top_clim_performers, aes(label=Strain), col = "black", size=3) +
#  geom_line(data=top_clim_performers, aes(group = Strain, color = Condition), alpha = 0.5) +
#  geom_text_repel(data=top_nlim_performers, aes(label=Strain), col = "black", size=3) +
#  geom_line(data=top_nlim_performers, aes(group = Strain, color = Condition)) +
#  geom_line(data=low_nlim_performers, aes(group = Strain, color = Condition)) +
#  geom_line(data=low_clim_performers, aes(group = Strain, color = Condition))
 
j2 <- ggplot(filter(violin_PW_GR, Condition %in% c("Clim", "Nlim", "Switch")), aes(x = as.factor(Time.Sim), y = Variance, color = Condition, group = 1)) +
  geom_point() +
  stat_summary(geom="line") +
  facet_wrap(~Condition) +
  xlab("Time (hrs)") +
  scale_color_manual(values = c(Clim_col, Nlim_col, Switch_col)) +
  theme(strip.background = element_blank(), strip.text.y = element_blank())

j <- j1 + j2 + plot_layout(ncol=1,heights=c(2,2))

ggsave(plot = j, height=4, width=10, dpi=200, filename="/Users/farah/Google Drive/Abdul-Rahman et al Barseq/figures/Figure5/Figure5AB.pdf", useDingbats=FALSE)

```

# What fraction of oscillating genotypes are 
```{r}
violin_PW_GR_spread <- violin_PW_GR %>%
  dplyr::select(-Variance) %>%
  spread(Condition, GR) %>%
    filter(Model != "NA") %>%
      mutate(Model = fct_relevel(Model, c("Non-Significant", "Linear", "Quadratic", "Cubic", "Periodic")))


ggplot(violin_PW_GR_spread, aes(x = Avg_CN, y = Switch, color = Model)) +
  geom_point(alpha = 0.1) +
  ylim(-0.4, 0.4) +
  xlim(-0.4, 0.4) +
  facet_wrap(~Time.Sim)

#piecewise growth rate distribution by model
j3 <- ggplot(violin_PW_GR_spread, aes(x = Model, y = Switch, color = Model)) +
  geom_boxplot() +
  ylab("Piecewise fitness in Switch") +
  xlab("Behavior") +
  scale_color_viridis(discrete = TRUE) +
  theme(axis.text.x = element_text(angle = 45, h = 1))
  
#j <- j1 + j2 + plot_layout(ncol=1,heights=c(2,2))

j <- j1 + 
  j2 + {
    j3 +
      plot_layout(ncol=1)
} +
  plot_layout(ncol=1)

ggsave(plot = j3, height=4, width=4, dpi=200, filename="/Users/farah/Google Drive/Abdul-Rahman et al Barseq in fluctuating environments/figures/Figure5/Figure5C.pdf", useDingbats=FALSE)
```

#What is the GO-tern enrichment of the highest growth rates in 
```{r}
heatmap_df1 <- violin_PW_GR %>%
  dplyr::filter(Model == "Periodic", Condition == "Switch") %>%
    dplyr::select(-Model, -Condition, -Variance) %>%
      spread(Time.Sim, GR)


heatmap_df <- as.data.frame(heatmap_df1[, -c(1, 2)])
rownames(heatmap_df) <- heatmap_df1$Strain
scaled_heatmap_mat <- as.matrix(scale(heatmap_df))

pdf("/Users/farah/Google Drive/Abdul-Rahman et al Barseq in fluctuating environments/figures/Figure5/Figure5D.pdf")
heatmap(scaled_heatmap_mat, scale = "none", Colv=NA, keep.dendro=TRUE, labRow = "")
dev.off()

#Test for legend, delete if not
pdf("/Users/farah/Google Drive/Abdul-Rahman et al Barseq in fluctuating environments/figures/Figure5/Figure5D-2.pdf")
heatmap.2(scaled_heatmap_mat, Rowv = TRUE, scale = "none", Colv=NA, dendrogram = "row", trace="none", density.info = "none")
dev.off()
###################

row.clusters = as.hclust( j4$Rowv )
eval(h$call)

Periodic_Clusters <- as.data.frame(cutree(row.clusters,h=9)) # break into k=3 clusters```

#Merge by rownames
Periodic_clustered_merged <- merge(scaled_heatmap_mat, Periodic_Clusters, by = 0)
colnames(Periodic_clustered_merged)[12] <- "Cluster"

Clust2_4 <- Periodic_clustered_merged %>%
  filter(Cluster %in% c("2", "4"))
    
rownames(Clust2_4) <- Clust2_4$Row.names
Clust2_4_heatmap <- as.matrix(Clust2_4[,-c(1,12)])
h2 <- heatmap(Clust2_4_heatmap, scale = "none", Colv=NA, keep.dendro=TRUE)

Clust1_3 <- Periodic_clustered_merged %>%
  filter(Cluster %in% c("1", "3"))
    
rownames(Clust1_3) <- Clust1_3$Row.names
Clust1_3_heatmap <- as.matrix(Clust1_3[,-c(1,12)])
h2 <- heatmap(Clust1_3_heatmap, scale = "none", Colv=NA, keep.dendro=TRUE)

write.csv(Clust1_3, "/Users/farah/Desktop/Clust1_3.csv")
